Title: A proof-of-concept study

### 2022-01-06 paper.tex
update

\begin{document}
\title{The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study}

@@

\subsection{Inclined jet injection}
  Early observation \citep{Gallimore2006} has proposed that\
  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
  A number of galaxies in which the jets are inclined to the disc normal\
  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{The slice of ...}
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

>>>>

\begin{document}
\title{Title: A proof-of-concept study}

@@

\subsection{Inclined jet injection}
  Early observation \citep{Gallimore2006} has proposed that\
  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
  A number of galaxies in which the jets are tilted to the disc normal\
  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet source show that the dense disk not only helps the bubbles to align the disk normal\
             but also create an under pressure, cold, and dense bubble in the most inner region.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}
